\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 1 (15\%) - Website Evaluation}\\
\end{flushleft}

In this assignment you are required to carry out a detailed assessment of five websites. Your assessment should include, but is not limited to, the following criteria:


\begin{enumerate}
	\item First Impressions
	\item Navigation
	\item Content
	\item Attractors
	\item Find-ability
	\item Making Contact
	\item Browser Compatibility
	\item Knowledge of Users
	\item User Satisfaction
	\item Other Useful Information
\end{enumerate}

Your assessment should take the form of a typewritten report explaining your findings in detail. In order to ensure you make an objective assessment you are strongly advised to create your own scoring model for your assessment criteria. You are encouraged to use an on-line tools for checking browser and device compatibility.\\

Your report should be laid out in a professional manner, as would be done for a client. This involves, \textit{inter-alia}, a cover page, table of contents, and logical sectioning.\\

The websites you are required to assess are:\\

\begin{enumerate}
	\item \href{http://www.world-bbq.com/}{http://www.world-bbq.com/}
	\item \href{http://irishbbqassociation.com/}{http://irishbbqassociation.com/}
	\item \href{http://www.americanbbq.org/}{http://www.americanbbq.org/}
	\item \href{http://ausbbqsociety.com/}{http://ausbbqsociety.com/}
	\item \href{http://www.bbqpr.com/}{http://www.bbqpr.com/}
\end{enumerate}

Your completed document is to be a single pdf file uploaded on or before the date and time as published on Moodle.\\

\vspace{1cm}
\textbf{Late Submission}\\
Failure to submit your assignment on or before the date and time indicated on Moodle will result in a penalty of 5\% per day or part thereof.
\\
\\
Late submission penalties will not apply in cases where a valid medical certificate is provided.  In such instances an extension of time will be granted for the duration of illness stated on the medical certificate that falls after the submission date.  A copy of the medical certificate must be included with the late submission.
\\
\\
Late submission penalties may also be avoided in exceptional circumstances.  These will be dealt with on a case by case basis.  Please note that loss of pen-drives, inability to use or access the software etc. will not be considered 'exceptional circumstances'.\end{document}